\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.5in]{geometry}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=cyan,
    urlcolor=cyan,
}

% --- ATS OPTIMIZATION NOTES ---
% Using standard, single-column format for easy parsing. [8]
% Avoiding complex tables, graphics, and unconventional fonts. [3]
% Ensuring key information is in the main body, not headers/footers.

% Custom colors
\definecolor{primary}{HTML}{2b2b2b}
\definecolor{secondary}{HTML}{565656}

% Custom itemize settings
\setlist[itemize]{
    leftmargin=20pt,
    itemsep=0pt,
    parsep=2pt,
    topsep=0pt,
    partopsep=0pt,
    labelsep=5pt
}

% Custom tighter itemize with indentation
\newenvironment{tightitemize}{
  \begin{itemize}[leftmargin=25pt, itemsep=2pt, parsep=2pt, topsep=2pt, partopsep=0pt]
}{
  \end{itemize}
}

% Spacing commands
\newcommand{\compactspace}{\vspace{6pt}}
\newcommand{\sectiongap}{\vspace{14pt}}

% Header
\newcommand{\header}[2]{
    \begin{center}
        {\Huge \textbf{#1}} \\
        \compactspace
        {\medium #2}
    \end{center}
}

% Section styling
\newcommand{\resumesection}[1]{
    \sectiongap
    {\color{primary} \large \textbf{#1}} \\
    \hrule height 1pt \compactspace
}

\begin{document}

% ===== HEADER =====
\header{D B Abhishek Anantapalli}
{+91 8317618694 \hspace{8pt}• \href{mailto:abhishekanantapalli@gmail.com}{abhishekanantapalli@gmail.com} \hspace{8pt}• 
\href{https://www.linkedin.com/in/abhishekanantapalli/}{\textcolor{cyan}{LinkedIn}} \hspace{8pt}• 
\href{https://github.com/AbhiAnantapalli215}{\textcolor{cyan}{GitHub}}}

% ===== PROFESSIONAL SUMMARY =====
\resumesection{PROFESSIONAL SUMMARY}
Detail-oriented Computer Science student with a Bachelor's degree and practical experience in C++, Python, and Java. Proven ability to develop software applications in Unix/Linux environments, with a strong foundation in distributed systems, machine learning, and information retrieval. Eager to solve complex challenges and contribute to projects utilizing artificial intelligence, natural language processing, and advanced search technologies.

% ===== EDUCATION =====
\resumesection{EDUCATION}
\textbf{Sri Vasavi Engineering College, Tadepalligudem} \hfill \textbf{2022--Present} \\
\indent Bachelor of Technology (B.Tech) in Computer Science and Engineering • CGPA: 9.15/10

\compactspace
\textbf{JNV Pedavegi, Eluru} \hfill \textbf{2019--2022} \\
\indent Intermediate (+2): 93\% • SSC: 86\%

% ===== TECHNICAL SKILLS =====
\resumesection{TECHNICAL SKILLS}
\begin{itemize}
    \item \textbf{Programming Languages}: \textbf{C, C++, Java, Python}
    \item \textbf{Core Competencies}: \textbf{Distributed Systems, Machine Learning, Artificial Intelligence, Natural Language Processing (NLP), Information Retrieval, Search Technologies}, Data Structures, Algorithms
    \item \textbf{Environments \& Protocols}: \textbf{Unix/Linux, TCP/IP}
    \item \textbf{Web Technologies}: React, Flask, JavaScript, HTML/CSS, Bootstrap
    \item \textbf{Tools \& Platforms}: Git, GitHub, Firebase, MySQL
    \item \textbf{Relevant Coursework}: Data Structures, Object-Oriented Programming, Operating Systems, Database Management Systems, Computer Networks
\end{itemize}

% ===== PROJECTS =====
\resumesection{PROJECTS}

\textbf{Attrisense — HR Analytics Dashboard} \hfill 
\href{https://github.com/AbhiAnantapalli215/Attrisense}{\textcolor{cyan}{GitHub}} \textbar\ 
\href{https://attrisense.web.app}{\textcolor{cyan}{Live}}
\begin{tightitemize}
    {\leftskip=12pt
        \item Researched and developed a React-based dashboard to improve on HR product offerings, utilizing \textbf{Artificial Intelligence} to provide predictive analytics.
        \item Contributed to a project focused on \textbf{scalability issues} by designing a system to handle large volumes of employee data and information.
        \item Integrated a \textbf{Machine Learning} model (scikit-learn) to identify attrition risks, extending the application's core features.
        \item Solved the problem of inefficient data access by creating a paginated employee directory with effective search and filtering capabilities.
        \item \textit{Tech Stack:} React, Firebase, JavaScript, Python, \textbf{Machine Learning} (scikit-learn)
    \par}
\end{tightitemize}

\textbf{E-commerce Website Clone — A Study in Search Technologies} \hfill 
\href{https://github.com/AbhiAnantapalli215/amazon-clone}{\textcolor{cyan}{GitHub}}
\begin{tightitemize}
    {\leftskip=12pt
        \item Developed a front-end clone to conceive and explore core e-commerce functionalities, focusing on product \textbf{search technologies}.
        \item Implemented key features for effective \textbf{information retrieval}, allowing users to search and filter through a third-party product API.
        \item Collaborated on solving UI/UX challenges to ensure responsive and scalable access to data across different devices.
        \item \textit{Tech Stack:} React, HTML, CSS, Bootstrap, REST APIs
    \par}
\end{tightitemize}




% ===== INTERNSHIPS =====
\resumesection{INTERNSHIPS}
\textbf{AWS Cloud Internship – BrainOvision Solutions Pvt. Ltd.} \hfill \textbf{Jan 2024 -- Mar 2024}
\begin{tightitemize}
    {\leftskip=15pt
        \item Gained hands-on experience with foundational components of \textbf{distributed systems} using AWS services (EC2, S3, VPC).
        \item Collaborated on team projects involving cloud infrastructure, focusing on the principles of scalable software applications.
        \item Worked within a \textbf{Unix/Linux environment} for server management and deployment tasks.
    \par}
\end{tightitemize}

% ===== CERTIFICATIONS =====
\resumesection{CERTIFICATIONS}
\begin{itemize}
    \item \textbf{Computer Networks \& Internet Protocol (NPTEL)} — Score: 83\% \hfill Jan--Apr 2024
    \item \textbf{Cybersecurity and Privacy (NPTEL)} — Score: 70\% \hfill Jul--Oct 2024
    \item \textbf{AWS Cloud Training (BrainOvision)} — Internship-based \hfill Jan--Mar 2024
\end{itemize}

% ===== ACHIEVEMENTS =====
\resumesection{ACHIEVEMENTS}
\begin{itemize}
    \item 2nd Prize – BrainOvision Hackathon on AWS fundamentals (College-level, 2023)
    \item 3rd Prize – SVEC Hackathon on Web Development (College-level, 2025)
    \item \textbf{LeetCode}: Solved 200+ problems involving data structures, algorithms, and distributed system concepts.
    \item \textbf{GeeksforGeeks}: Solved 500+ problems, strengthening programming skills in \textbf{C++, Java, and Python}.
\end{itemize}

\end{document}